### 2017-10-22 paper/sections/6_results.tex
paper: intro to the evaluation
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We did not compare to other HPC systems because we are not claiming that our
file system metadata protocols are superior. Instead, we use Ceph as a platform
for exploring related work over the same storage system, which facilitates an
apples-to-apples comparison of the strategies themselves.  So we run
experiments on the same cluster and normalize results to control for hardware
differences and to make our results more generally applicable.  Our goal is not
to build a file system optimized for HPC workloads and our prototype is not a
competitor to Lustre. Rather it is a solution for letting the techniques of a
system like Lustre live in the same namespace as techniques optimized for file
creates, like BatchFS.

@@

We evaluate our prototype on the two clusters in Table~\ref{table:clusters}.
Microbenchmarks were run on the in-house clusters while client scalability
tests were run on CloudLab. We only scale up to 29 clients because that is the
maximum capacity of a single metadata server. For the in-house cluster, we need
more object storage servers and we have to co-locate clients on the same node
because of resource contention \footnote{The bandwidth to RADOS is only
sufficient with 8 nodes on this older hardware, which uses SSDs and nodes that
are almost 10 years old.  The CloudLab cluster performs just as well with and
without a highly provisioned object storage server cluster.}. All daemons run
as a single process which is the default setting for Ceph. We develop on Ceph's
Jewel release, version 10.2.1, which was released in May 2016.

>>>>

Cudele lets users construct consistency/durability guarantees using
well-established research techniques from other systems; so instead of
evaluating the scalability and performance of the techniques
themselves\footnote{ This is the reason we did not compare to other HPC or data
center systems; we are not claiming that our file system metadata protocols are
superior.}, we show that (1) the mechanisms we propose are useful for
constructing semantics used by real systems, (2) the techniques can work
side-by-side in the same namespace, and (3) the combination of these techniques
can help the system scale farther when subtrees are coupled to the correct type
of application.  We scope the evaluation to one metadata server and scale the
clients, which execute an extremely metadata intensive job in parallel. This
type of analysis shows the capacity and performance of a metadata server with
superior metadata protocols, which should be used to inform load balancing
across a metadata cluster. Load balancing with partitioning and replication can
be explored with something like Mantle~\cite{sevilla:sc15-mantle}.

@@

We evaluate our prototype on the two clusters in Table~\ref{table:clusters}.
Microbenchmarks were run on the in-house clusters while client scalability
tests were run on CloudLab. We only scale up to 29 clients because that is the
maximum capacity of a single metadata server. For the in-house cluster, we need
more object storage servers and we have to co-locate clients on the same node
because of resource contention \footnote{The bandwidth to RADOS is only
sufficient with 8 nodes on this older hardware, which uses SSDs and nodes that
are almost 10 years old.  The CloudLab cluster performs just as well with and
without a highly provisioned object storage server cluster.}. All daemons run
as a single process which is the default setting for Ceph. We develop on Ceph's
Jewel release, version 10.2.1, which was released in May 2016.  We run
experiments on the same cluster and normalize results to control for hardware
differences and to make our results more generally applicable.
